CODE CHECK

### 2020-06-29 codecheck-paper.Rmd
Update codecheck-paper.Rmd

- Do publishers need to build up data science experts who can conduct checks?
- Is an integration of software/data citation checks benefitial/realistic?
- Bot-support and tools (linter, report authoring with R Markdown)
- How can open platforms be used to enable a review in private (cf. https://www.cambridge.org/core/blog/2019/08/19/how-to-make-the-data-and-code-for-your-manuscript-available-to-peer-reviewers-before-making-it-public/), if that is desired
- Does nudging towards better practices work (highlight the successes) or is any check with opt-in doomed to fail?
- Do we need more than one codechecker? Is there a similar diversity as in a peer review where more opinions are needed?
- can CODECHECK work for preprints? how? is a re-check required?
- Risk: is the hurdle too low? are "levels" of checks are solution to increase transparency of check's level of detail
- CODECHECK in the context of innovations and disruptions in scientific publishing
  - https://doi.org/10.1042/ETLS20180172
  - https://doi.org/10.3390/publications7020034
- Should every code be checkd, or should the labour be capped by only checking "important" works or at important stages; if yes, isn't peer review such a stage?
- see https://github.com/codecheckers/discussion
- Can we establish code checks as a type of review within the schol comm metadata (or should we?) > we should not, put them on the same level as reviews!
- How can we turn a CODECHECK into a positive experience?
  - cf. kindness in peer review in https://www.mdpi.com/2304-6775/8/2/26
- How can we allow reactions to checks? (commenting on reports)
- Will bitwise reproducibility become easier than what a CODECHECK does? triggered by https://twitter.com/khinsen/status/1242842759733665799?s=09)

>>>>

- Do publishers need to build up data science experts who can conduct checks?
- Is an integration of software/data citation checks benefitial/realistic?
- Bot-support and tools (linter, report authoring with R Markdown)
- How can open platforms be used to enable a review in private (cf. https://www.cambridge.org/core/blog/2019/08/19/how-to-make-the-data-and-code-for-your-manuscript-available-to-peer-reviewers-before-making-it-public/), if that is desired
- Does nudging towards better practices work (highlight the successes) or is any check with opt-in doomed to fail?
- Do we need more than one codechecker? Is there a similar diversity as in a peer review where more opinions are needed?
- can CODECHECK work for preprints? how? is a re-check required?
- Risk: is the hurdle too low? are "levels" of checks are solution to increase transparency of check's level of detail
- CODECHECK in the context of innovations and disruptions in scientific publishing
  - https://doi.org/10.1042/ETLS20180172
  - https://doi.org/10.3390/publications7020034
- Should every code be checkd, or should the labour be capped by only checking "important" works or at important stages; if yes, isn't peer review such a stage?
- see https://github.com/codecheckers/discussion
- Can we establish code checks as a type of review within the schol comm metadata (or should we?) > we should not, put them on the same level as reviews!
- How can we turn a CODECHECK into a positive experience?
  - cf. kindness in peer review in https://www.mdpi.com/2304-6775/8/2/26
- How can we allow reactions to checks? (commenting on reports)
- Will bitwise reproducibility become easier than what a CODECHECK does? triggered by https://twitter.com/khinsen/status/1242842759733665799?s=09)
- If a report is not published for failures: Isn't there a bias for the codechecker to have a "successful" reproduction because then a report is published?
